\section{Data Collection Methods}


In this study we did four interviews where two interviewers interacted with a single student. Four students were interviewed in total.
For each interview, a student was given four different problems. Each interview took between 40 minutes and 1 hour to complete.
After they felt comfortable with the answer to their problem,
 the interviewers asked the student questions about the problem to gather more information on how they solved the problem,
 and how thoroughly they understood various sections of the provided code.
For each interview, the student's actions and voice were recorded, and then transcribed and analyzed afterwards. \\

Though the participants all had taken basic programming courses, there were a variety of backgrounds.
None of the students had completed the Programming Languages class, where topics such as functional programming are covered in depth.
However, all of the students had been exposed to Python syntax and list, as well as the map function in Python.
In this paper we focused on one participant who also had tutoring experience for a course in program development and data structures. \\

The four problems were split up into two evaluation problems and two debugging problems.
For the evaluation problems, the student was instructed to evaluate the Python code given to them.
For the debugging problems, the student was informed of the unwanted (buggy) behavior,
 although for the first debugging problem it was asked whether the behavior occurred (which it did),
 and for the second the student was told that the behavior occurred and was asked to find a solution.
The students were encouraged to talk out loud and informed that they could write on the paper.
Finally, the interviewers answered questions that could be reasonably inferred from a Google search, such as,
``is \_\_init\_\_ a constructor?''
However, questions specific to the code were not answered, and when students felt confidant in their solution we accepted it independent of correctness.
If it became clear that a student was not making progress, hints were supplied, however this did not happen in any of the interviews we analyzed.

% fix after peer review
%\newpage